### 2017-01-12 MSSM/MSSM.tex
Fixing tables in MSSM section

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
\end{center}
\caption{\mTtot~ distribution in the \ttbar enriched control region.
The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
\label{fig:mssm_corrs_toppt}
\end{figure}

@@

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_ggH.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_bbH.pdf}}
\end{center}
\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
while the \tautau channel dominates for higher masses. The \etau channel is always
slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive.}
\label{fig:mssm_results_limits_breakdown_hig16006}
\end{figure}

\subsection{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in 2015 and 2016 need to be taken into account.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
The correlation scheme between nuisance parameters relating to the 2015 and 2016
analyses, as used for this combination, is given in table ADD TABLE.

\begin{table}[htp]
\begin{center}
\caption{Correlations between nuisance parameters in 2015 and 2016 analysis}
\begin{tabular}{@{}lll@{}}
%\toprule
\textbf{Nuisance} & \textbf{Correlation} & \textbf{Motivation}\\
\midrule
Luminosity & Partially correlated & As studied by the relevant people in the experiment\\
Jet energy scale & Fully correlated & Found to be so by those responsible for it in the experiment\\
b-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods\\
mis-tagging & Part correlated & As recommended by those measuring b-tagging scale factors\\
Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016\\
Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016\\
Tau ID/isolation/trigger& Uncorrelated & On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis\\
High \pT tau ID efficiency & Correlated & This should not be affected by the lack of tau ID scale factor and covers teh same underlying issue in both analyses\\
Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
Drell-Yan shape & Correlated & The same \ac{MC} samples, exhibiting the observed discrepancies, is used. In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar\\
W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & Correction not applied in the 2016 dataset while it was applied for the 2015 analysis. The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point\\
MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016\\
Top quark \pT reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses\\
Drell-Yan cross section & Correlated & Theoretical uncertainty so should be correlated\\
Di--boson cross section & Correlated & Theoretical uncertainty so should be correlated\\
\ttbar cross section & Correlated & Theoretical uncertainty so should be correlated\\
\Wjets cross section & Correlated & Theoretical uncertainty so should be correlated\\
SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated\\
\Ztautau acceptance & - & Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet\\
\Ztautau extrapolation& - & Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance\\
e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\

\end{tabular}
\label{tab:mssm_combination_correlations}
\end{center}
\end{table}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mt_tot_ttcontrol_em_2016.png}
\end{center}
\caption{\mTtot~ distribution in the \ttbar enriched control region.
The uncertainty band includes the statistical uncertainty as well as a 6\% \ttbar cross--section uncertainty.}
\label{fig:mssm_corrs_toppt}
\end{figure}

@@

\subsection{Summary of uncertainties and correlations}
\label{sec:mssm_uncs_summary}
The systematics that are applied are summarised in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
indicates that the uncertainty is correlated between categories but uncorrelated between
the different decay channels.
\input{MSSM/UncOv}
\clearpage

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_ggH.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/mssm_hig16006_limitcomp_bbH.pdf}}
\end{center}
\caption{Expected upper limits at 95\% CL for (a) gluon--gluon fusion and (b) b--associated production,
comparing the combination of all channels (green) with the \mutau (red), \etau (blue) \tautau (black)
and \emu (gold) channels. For masses below 200 GeV the \mutau channel is the most sensitive,
while the \tautau channel dominates for higher masses. The \etau channel is always
slightly less sensitive than the \mutau channel. The \emu channel is the least sensitive.}
\label{fig:mssm_results_limits_breakdown_hig16006}
\end{figure}
\clearpage

\subsection{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in 2015 and 2016 need to be taken into account.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
The correlation scheme between nuisance parameters relating to the 2015 and 2016
analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}.

\begin{table}[htp]
\begin{center}
\caption{Correlations between nuisance parameters in 2015 and 2016 analysis}
{\footnotesize
\begin{tabular}{p{3cm}p{2cm}p{10cm}}
\toprule
\textbf{Nuisance} & \textbf{Correlation} & \textbf{Motivation}\\
\midrule
Luminosity & Partially \mbox{correlated} & As studied by the relevant people in the experiment\\
\midrule
Jet energy scale & Fully \mbox{correlated} & Found to be so by those responsible for it in the experiment\\
\midrule
b-tagging & Uncorrelated & Scale factors used in 2015 and 2016 analysis measured via different methods\\
\midrule
mis-tagging & Partially \mbox{correlated} & As recommended by those measuring b-tagging scale factors\\
\midrule
Muon ID/isolation/trigger & Uncorrelated & The 2015 and 2016 analyses use different muon ID and isolation working points, and the \ac{L1} trigger was replaced completely between 2015 and 2016\\
\midrule
Electron ID/isolation/trigger & Uncorrelated & The \ac{L1} trigger was completely replaced between 2015 and 2016\\
\midrule
Tau ID/isolation/trigger& Uncorrelated & \scriptsize{On top of the replacement of the \ac{L1} trigger, a tau ID scale factor was applied in the 2016 analysis but not in the 2015 analysis, despite the fact that the yield should have been brought down by around 8\% for the 2015 analysis}\\
\midrule
High \pT tau ID efficiency & Correlated & This should not be affected by the lack of tau ID scale factor and covers teh same underlying issue in both analyses\\
\midrule
Tau energy scale & Correlated & There is no reason to expect a different best-fit energy scale between 2015 and 2016\\
\midrule
Drell-Yan shape & Correlated & \scriptsize{The same \ac{MC} samples, exhibiting the observed discrepancies, are used. In addition the weights as derived for the 2015 analysis and the 2016 analysis are very similar}\\
\midrule
W jet$\rightarrow\Pgt_{h}$ fake rate shape & Uncorrelated & \scriptsize{Correction not applied in the 2016 dataset while it was applied for the 2015 analysis. The uncertainties have a different functional form, possibly due to different jet$\rightarrow\Pgt_{h}$ fake rates as a result of the use of a different tau isolation working point}\\
\midrule
MET uncertainties & Correlated & The same MVA \MET training was used both for 2015 and 2016\\
\midrule
Top quark \pT reweighting & Correlated & The same corrections were applied to the 2015 and 2016 analyses\\
\midrule
Drell-Yan $\sigma$& Correlated & Theoretical uncertainty so should be correlated\\
\midrule
Di--boson $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
\midrule
\ttbar $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
\midrule
\Wjets $\sigma$ & Correlated & Theoretical uncertainty so should be correlated\\
\midrule
SM signal theory uncertainties & Correlated & Theoretical uncertainties so should be correlated\\
\midrule
\Ztautau \mbox{acceptance} & N/A & \scriptsize{Uncertainty only exists in 2015 analysis as no fits to the \Zmm control region were included yet.}\\
\midrule
\Ztautau \mbox{extrapolation}& N/A & \scriptsize{Uncertainty only exists in 2016 analysis as fits to the \Zmm control regions were included and this uncertainty should cover only the extrapolation from \Zmm to \Ztautau, not the full acceptance.}\\
\midrule
%e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
%$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
%jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
%QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-iso sideband in 2015 and 2016 analyses\\
%QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
%Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
%Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
%Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region. In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that\\
%Statistical uncertainty on W low/high\mT~ ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
%Systematic uncertainty on W low/high\mT~ ratio (\etau and \mutau) & Uncorrelated & This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately\\
%QCD OS/SS ratio statistical uncertainty (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated\\
%QCD OS/SS ratio systematic uncertainty (\etau and \mutau) & Uncorrelated & The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses. Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.\\
%bin--by--bin uncertainties for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible to achieve\\
\end{tabular}}
\label{tab:mssm_combination_correlations}
\end{center}
\clearpage
\end{table}
\begin{table}[pt!]
\begin{center}
{\footnotesize
\begin{tabular}{p{3cm}p{2cm}p{10cm}}
\midrule
e$\rightarrow\Pgt_{h}$ fake rate & Correlated & Expect to behave the same in 2015 and 2016 datasets\\
\midrule
$\mu\rightarrow\Pgt_{h}$ fake rate & Uncorrelated & Measurement had not been made at time of 2015 analysis and so no scale factors were applied yet\\
\midrule
jet$\rightarrow\Pgt_{h}$ fake rate & Correlated & ....\\
\midrule
QCD extrapolation uncertainty (\emu channel) & Uncorrelated & Use of slightly different anti-iso sideband in 2015 and 2016 analyses\\
\midrule
QCD normalisation uncertainty (\tautau channel) & Uncorrelated & Use of different anti-isolated sideband\\
\midrule
Parameters tying control regions to signal region normalisations & Uncorrelated & 2016 control region fits should not influence the 2015 SR and vice versa\\
\midrule
Statistical uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
\midrule
Systematic uncertainty on W opposite--sign to same--sign ratio (\etau and \mutau)& Uncorrelated & \scriptsize{Uncertainty based on high \mT~ region with anti-isolated $\Pgt_{h}$, but because of the tau \pT~ cuts being different in 2015 and 2016 analyses we could expect a different event composition in this region. In addition this uncertainty was already uncorrelated between channels and categories in each individual analysis, and we can't claim to know the correlation between the two years any more accurately than that.}\\
\midrule
Statistical uncertainty on W low/high\mT~ ratio (\etau and \mutau)& Uncorrelated & Statistical uncertainties should not be correlated\\
\midrule
Systematic uncertainty on W low/high\mT~ ratio (\etau and \mutau) & Uncorrelated & \scriptsize{This was already uncorrelated between channels and categories in each individual analysis, we can't claim to know the correlation between the two years any more accurately}\\
\midrule
QCD OS/SS ratio statistical uncertainty (\etau and \mutau) & Uncorrelated & Statistical uncertainties should not be correlated\\
\midrule
QCD OS/SS ratio systematic uncertainty (\etau and \mutau) & Uncorrelated & \scriptsize{The ratios were measured in different anti-isolated sidebands, and with different $\Pgt_{h}$ \pT~ selections, in the two analyses. Same comments about the correlations between channels and categories within the individual analyses as for the W systematic uncertainties apply.}\\
\midrule
bin--by--bin uncertainties for templates with low numbers of events & Uncorrelated &Because the same initial \ac{MC} simulation was used these should in theory be correlated, in practice this is unfeasible to achieve\\
\bottomrule
\end{tabular}}
\end{center}
\end{table}
\clearpage

### 2017-01-12 MSSM/UncOv.tex
Fixing tables in MSSM section

\section{Overview of uncertainties}
\label{sec:mssm_uncs_overview}
The systematics that are applied are summarised in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}.

@@

or background events in the $\mu \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}

@@

@@

    \hline

@@

    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Corr. between cats, uncorr. between chns    \\
    \hline

@@

    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Corr. between cats, uncorr. between chns   \\
    \hline

@@

    \multicolumn{10}{l}{\textbf{Normalisation,} $\cPqt\cPaqt$}\\

@@

    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Corr. between cats, uncorr. between chns        \\

@@

    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Corr. between cats, uncorr. between chns  \\
    \hline

@@

    \hline

@@

or background events in the $e \tau_{h}$ channel. Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}

@@

    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Corr. between cats, uncorr. between chns       \\

@@

or background events in the $\tau_{h} \tau_{h}$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}

@@

\begin{tabular}{l|cc|p{3cm}}

@@

    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\

@@

@@

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the $e\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \hline
    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \hline
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \hline
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories.}
{\scriptsize
\begin{tabular}{l|cc|p{3cm}}
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \hline
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \hline
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \hline
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \hline
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \hline
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \hline
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \hline
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \hline
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, }$\cPqt\cPaqt$}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \hline
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}

>>>>

@@

or background events in the $\mu \tau_{h}$ channel.} 
 {\tiny

@@

\toprule

@@

    \midrule

@@

    ZTT,TTT,VVT, signal     & 3\% & 3\% & 3\% & 3\%   & 3\%  & 3\% & 3\% & 3\% & Cats:C,chns:U    \\
    \midrule

@@

    ZTT,TTT,VVT, signal     & shape & shape & shape & shape  & shape & shape & shape & shape & Cats:C,chns:U   \\
    \midrule

@@

    \multicolumn{10}{l}{\textbf{Normalisation,} \ttbar}\\

@@

    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% &Cats:C,chns:U        \\

@@

    ZJ,TTJ     & 20\%  & 20\% &20\% &20\%      & 20\% & 20\% &20\% &20\%  & Cats:C,chns:U  \\
    \midrule

@@

\bottomrule

@@

or background events in the \etau channel.}
 {\tiny

@@

    ZL     & 30\%  & 30\% & 30\% & 30\%   & 30\% & 30\% & 30\% &30\% & Cats:C,chns:U       \\

@@

or background events in the \tautau channel.}

@@

\begin{tabular}{l|cc|p{5cm}}
\toprule

@@

    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\

@@

\bottomrule

@@

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of signal
or background events in the \emu channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC      & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron identification and trigger}}\\
    All from MC       & 2\%        & 2\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}  }\\
    All from MC      & 2\%     & 2\%  & Fully correlated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Electron energy scale}} \\
    ZTT,signal      & shape      & shape  & Fully correlated                \\
    \midrule
    \multicolumn{4}{l}{\textbf{DY reweighting }}\\
     ZTT       & shape      & shape & Fully correlated                       \\
   \midrule
    \multicolumn{4}{l}{\textbf{Top quark} $P_{T}$ \textbf{reweighting}}\\
    TT & shape & shape  & Fully correlated                 \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }$\PZ$ \textbf{production} }\\
    ZLL      & 4\%      & 4\%  & Fully correlated                   \\
    \midrule
    \multicolumn{4}{l}{$Z\to\Pgt\Pgt/Z\to\Pgm\Pgm$\textbf{: extrapolation} }\\
     ZTT        & 3\%        & 5\%   & Fully uncorrelated                      \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, QCD multijet }}\\
    QCD & 23\% & 34\% & Fully uncorrelated\\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
\bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_em}
\end{center}
\end{table}

\begin{table}[!h]
\begin{center}
\caption{Systematic uncertainties that affect the estimated number of
or background events in the $Z\rightarrow\mu\mu$ channel.}
{\scriptsize
\begin{tabular}{l|cc|p{5cm}}
   \toprule
     & \multicolumn{2}{|c}{Event yield uncertainty by event category} &   \\
    \midrule
    \textbf{Process}
    &  \textbf{No b-tag} & \textbf{B-tag} & \textbf{Correlation}                   \\
    \midrule
    \multicolumn{4}{l}{\textbf{Integrated luminosity 13}\TeV}\\
    All from MC (not ZL)     & 6.2\%      & 6.2\% & Fully correlated                            \\
    \midrule
    \multicolumn{4}{l}{\textbf{Jet energy scale}}\\
    All from MC   & 0--1\% & 1--69\% &Fully correlated \\
    \midrule
    \multicolumn{4}{l}{\MET \textbf{scale}} \\
    ZTT,W    & 2\%     & 2\% & Correlated between chn/cat,                          \\
    TT,VV    & 2\%     & 2\% & ZTT,W uncorrelated from TT,VV \\
    \midrule
   \multicolumn{4}{l}{ \MET \textbf{resolution}} \\
    ZTT,W & 2 \%    & 2\%  & Correlated between chn/cat,\\
    TT,VV & 2\%     & 2\%  & ZTT,W uncorrelated from TT,VV\\
    \midrule
    \multicolumn{4}{l}{\textbf{Muon identification and trigger}}\\
    All from MC       & 2--4\%        & 2--4\% & Fully correlated                              \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-tagging efficiency}} \\
    All from MC     & 0--3\%     & 1--3\%  & Fully correlated                  \\
    \midrule
    \multicolumn{4}{l}{\textbf{B-mistag rate}}\\
    All from MC      &     & 0--10\% & Fully correlated                    \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, }\ttbar}\\
    TT        & 6\%       & 6\% & Fully correlated                        \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, di-boson}} \\
    VV        & 5\%       & 5\% & Fully correlated                       \\
    \midrule
    \multicolumn{4}{l}{\textbf{Normalisation, W + jets }}\\
    W+jets & 4\% & 4\% & Fully correlated\\
    \bottomrule
\end{tabular}}
\label{tab:SystematicUncertainties_zmm}
\end{center}
\end{table}
